### 2020-01-29 msr.tex
msr chapter edits

The \gls{MSFR} is a reference fast-spectrum \gls{MSR} concept developed
under the \gls{EVOL} project. Inspired by the \gls{MSBR}, the \gls{MSFR} is
intended to run primarily on a closed thorium fuel cycle with
continuous online fuel reprocessing. Several reasons motivated the omission of
graphite moderators from the \gls{MSFR} design. Graphite is susceptible to
long-term radiation damage and replacement is likely to be necessary during
the operating lifetime of the reactor. The fast neutron spectrum improves
breeding ratios due to higher fission neutron yield in $^{233}$U and lower
parasitic absorption in non-fuel materials. Lastly, graphite has a positive
temperature coefficient of reactivity; eliminating graphite from the design
ensures a greater safety margin.

Power output of the \gls{MSFR} is rated at 3000 MW$_{\text{th}}$ and 1500
MW$_{\text{e}}$. The high thermal efficiency is achieved

>>>>

The \gls{MSFR} is a reference fast-spectrum \gls{MSR} concept developed
under the \gls{EVOL} and \gls{SAMOFAR} projects. The main reactor
specifications and schematic view are shown in Table * and Fig. *
respectively. Inspired by the \gls{MSBR}, the \gls{MSFR} is
intended to run primarily on a closed thorium fuel cycle with
continuous online fuel reprocessing. Several reasons motivated the omission of
graphite moderators from the \gls{MSFR} design. Graphite is susceptible to
long-term radiation damage and replacement is likely to be necessary during
the operating lifetime of the reactor. The relatively fast neutron spectrum
improves breeding ratios due to higher fission neutron yield in $^{233}$U and
lower parasitic absorption in non-fuel materials. Lastly, graphite has a
positive temperature coefficient of reactivity; eliminating graphite from the
design ensures a greater safety margin.

In the \gls{MSFR} design, fuel salt flows upwards through a 9 m$^3$ central
core region. At the top of the core, the flow separates into 16 smaller
external loops, each of which passes through a heat exchanger before being
pumped back into the bottom of the core. Other instrumentation are situated
along the external loop for online salt reprocessing and gas sparging. The
core is surrounded axially by nickel alloy reflectors, and radially by a
toroidal blanket tank containing fertile salt for breeding. There is a layer
of boron carbide behind the blanket tanks to protect the peripheral equipment
from excessive neutron damage. In case of severe accidents, there is an
actively cooled freeze plug at the bottom of the core that melts when
temperatures exceed a certain threshold. The fuel salt would drain into a
containment vessel designed to keep it subcritical. Reactivity control under
normal operating conditions is performed by varying pump speeds to advantage
of strong thermal feedback. Coupled with the fact that there is no excess
reactivity reserve due to online fuel reprocessing, control rods are not
included in the \gls{MSFR}.

Although the \gls{MSFR} is primarily designed to operate on the thorium fuel
cycle, it can support a range of start-up fuel and feed compositions. This
versatility is particularly important for the first few \glspl{MSFR} to be
deployed due to the lack of $^{233}$U reserves required for the initial core
loading. In general, the fuel and blanket salts are approximately composed of
eutectic mixtures of 77.5\% LiF - 22.5\% AcF$_4$, where AcF$_4$ represents
actinide fluorides such as uranium, thorium, plutonium, and other \gls{TRU}
fluorides. For an initial composition consisting of $^{232}$Th and $^{233}$U,
the benchmark value for the amount of uranium for criticality under
normal operating conditions is 2.515 mol\%. However, most code verification
studies adjust the ratio of $^{232}$Th to $^{233}$U to achieve exact
criticality at a uniform temperature of 973 K; this ensures that subsequent
neutronics and safety analyses are not affected by the difference in
k$_{\textt{eff}}$ values. We performed the same exercise in this paper.

Power output of the \gls{MSFR} is rated at 3000 MW$_{\text{th}}$ and 1500
MW$_{\text{e}}$. It has a high thermal efficiency due to its high operating
temperature. \glspl{MSR} in general are not restricted by the same pressure
constraints seen in \glspl{LWR}. The inlet and outlet temperature
specifications of the fuel salt are 923 K and 1023 K respectively. This was
motivated by the need for a minimum 50 K temperature buffer between the
operating temperatures and the melting point of the salt. The \gls{MSFR} has
heat exchangers and an intermediate coolant loop to isolate the power
conversion system from the highly radioactive fuel salt. This also serves as
a layer of containment between the radioactive material and the outside
environment. The exact composition of the intermediate coolant is still under
active study and not finalized yet.
